%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%     File: Thesis_Abstract.tex                                        %
%     Tex Master: Thesis.tex                                           %
%                                                                      %
%     Author: Andre C. Marta                                           %
%     Last modified :  2 Jul 2015                                      %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Abstract}

% Add entry in the table of contents as section
\addcontentsline{toc}{section}{Abstract}

In modern software engineering, Continuous Integration (CI) has become an indispensable step towards managing systematically the life cycles of system development. Large companies struggle with keeping the pipeline updated and operational, due to the large amount of changes and addition of features, that build on top of each other. Associated with such software changes is a strong component of Testing. By selecting the most promising test cases quicker, the round-trip time between making a change and receiving feedback is shortened, boosting productivity. To alleviate this burden, two Test Case Prioritization algorithms were developed.

Extending the research of applying Reinforcement Learning to optimize Testing strategies. After proven to be a strategy as good as traditional methods, we test its ability to adapt to new environments, by using novel data from the financial industry.
Additionally, we studied the impact of experimenting a new model for memory representation: Decision Trees, without producing significant improvements relative to Artificial Neural Networks.
 
NNE-TCP is a Machine-Learning (ML) framework that analyses what files were modified when there was a test status transition and learns relationships between the two entities by mapping them into multidimensional vectors and grouping them by similarity. When new changes are made, tests that are more likely to be linked to the files modified are prioritized. Furthermore, NNE-TCP enables entity visualization in low-dimensional space, allowing for smarter groupings.
By applying NNE-TCP, it is shown for the first time that the modified files and tests connection is relevant and produces fruitful prioritization results.

\vfill

\textbf{\Large Keywords:} Continuous Integration, Regression Testing, Test Case Prioritization, Reinforcement Learning,  Embeddings, Data.

